TBD

### 2021-02-21 outputs/paper/paper.Rmd
Accidentally rolled back Chi-Sq tests - brought them back; also fixed table numbering issues

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

Pearson’s Chi-squared test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0 (*p* < 2.2e-16), meaning that there is a high correlation between those two variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
header-includes:
    - \usepackage[labelformat=empty]{caption}
toc: FALSE
bibliography: references.bib
---

@@

Pearson’s Chi-squared (*X*^2^) test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0 (*p* < 2.2e-16), meaning that there is a high correlation between those two variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.
